---
title: "Introduction to `RGgitP` Package"
author: RG9303
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RGgitP)
library(knitr)
```

## I. Introduction

This R package is the coursework from week 4 of Coursera: Building R Package. The package will utilize data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, and it is a nationwide census of the American public yearly data about motor vehicle traffic crashes. You can perform data and make graphic analysis. If you need more information you can visit https://crashstats.nhtsa.dot.gov/#/DocumentTypeList/23.

## II. Load data

1. If you want to create a FARS csv extension filename for the given year you can use `make_filename()`. If you need more information, type `?make_filename` in the R console.

```{r}

filename_2013 = make_filename(year = 2013)
print(filename_2013)

```


2. If you read the data with a given data you need to use `fars_read()`. If the data exist, it will return the dataframe; if the data does not exist, it will return ERROR. You find more information with `?fars_read` in the R console.

```{r}

fars_data = fars_read(filename = filename_2013)
head(fars_data)
names(fars_data)

```


## III. Read data with some years

You can read FARS data with some years using `fars_read_year()`. It function combines `make_filename()` and `fars_read()` to return a dataframe separate by the given year.  If the data corresponds to the given year does not exist, a WARNING will return. You find more information with `?fars_read_year` in the R console.

```{r}

fars_read_years(years = c(2013, 2014))

```



## III. Summary table 

If you need to create a summary table of data per month for the some given years with this dataframes, you can use `fars_summarize_years()`. If the data corresponds to the given year does not exist, an ERROR will return. If you need more details, type `?fars_summarize_years` in the R console.

```{r}

knitr::kable(fars_summarize_years(years = c(2013:2015))) 

```



### IV. Mapping data

You can display the data for a given state using state code and a given year. For more information regarding to state code, type `?fars_map_state` in the R console.

```{r}

fars_map_state(state.num = 06, year = 2013)
fars_map_state(state.num = 26, year = 2013)

```






